---
title: "Main area"
author: "Ronan Sharp, Lucas Karls, Noah Crawley, Joe Held"
date: "2024-04-05"
output: html_document
---
```{r}
library(tidyverse)
library(rvest)
url <- "https://www.imdb.com/list/ls006266261/?sort=list_order,asc&st_dt=&mode=detail&page="
html = read_html(url)



stuff = html_nodes(html, ".lister-item-header a") %>% html_attr("href")
head(stuff)
tt_stuff = stuff %>% str_extract(pattern = "tt\\d+")

str_c("https:www.imdb.com/title/", tt_stuff,"/fullcredits?ref_=tt_cl_sm")
```


```{r}
library(rvest)
library(stringr)
#Define the common part of the URL


common_url <- "https://www.imdb.com/list/ls006266261/?sort=list_order,asc&st_dt=&mode=detail&page="
# Extract the numbers from the common part of the URL

numbers <- 1:10

 

# Generate the complete URLs by joining the common part with the numbers

urls <- str_c(common_url, numbers)

 

# Initialize an empty vector to store all titles

all_titles <- c()
all_actors = c()
all_directors = c()
all_star = c()
all_profit = c()
# Loop through each URL

