The overall goal for this project was to create a contentedness graph for a group of actors and then find the "Bacon Number" (degree of separation from Kevin Bacon or another actor of choosing) between actors. 

\vspace{5cm}

## Movie Dataframe


- The first step in this project was to scrape the the top 1000 movies from the website IMDB and then create a data frame of this data. In order to do this, we had use the selector gadget, and were able to find the keywords associated with the information of each movie. We then were able to take the title, top 4 actors, directors, rating, and profit from each movie and put that data into our data frame. After further manipulation, we were able to assign the correct four actors to each movie, as well as all of the other information we selected to go with each movie. After doing this we were able to create a connectedness graph.

\vspace{4cm}  

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(rvest)
library(stringr)
library(dplyr)
library(igraph)
library(tidygraph)
library(tidyverse)
library(ggraph)
library(visNetwork)


# Define the common part of the URL
common_url <- "https://www.imdb.com/list/ls006266261/?sort=list_order,asc&st_dt=&mode=detail&page="

# Extract the numbers from the common part of the URL
numbers <- 1:10

# Generate the complete URLs by joining the common part with the numbers
urls <- str_c(common_url, numbers)

# Initialize empty lists to store all titles, actors, directors, ratings, and profits
all_titles <- c()
all_actors <- c()
all_directors <- c()
all_ratings <- c()
all_profits <- c()

# Loop through each URL
for (url in urls) {
  # Read HTML content of the webpage
  webpage <- read_html(url)
  
  # Find titles, actors, directors, ratings, and profits based on selector gadget key words
  titles <- webpage %>% html_nodes(".lister-item-index+ a")
  actors <- webpage %>% html_nodes(".ghost~ a , .mode-detail:nth-child(17) .text-small a")
  directors <- webpage %>% html_nodes(".text-muted a:nth-child(1)")
  ratings <- webpage %>% html_nodes(".ipl-rating-star.small .ipl-rating-star__rating")
  profits <- webpage %>% html_nodes(".ghost~ .text-muted+ span")
  
  # Extract text content of the nodes this then gives us the information we need for each of the categories
  titles_text <- titles %>% html_text()
  actors_text <- actors %>% html_text()
  directors_text <- directors %>% html_text()
  ratings_text <- ratings %>% html_text()
  profits_text <- profits %>% html_text()
  
  # Append titles, actors, directors, ratings, and profits to the vectors
  all_titles <- c(all_titles, titles_text)
  all_actors <- c(all_actors, actors_text)
  all_directors <- c(all_directors, directors_text)
  all_ratings <- c(all_ratings, ratings_text)
  all_profits <- c(all_profits, profits_text)
}

# Remove the directors that come up as actors to get all the actors consistant with each movie
all_actors <- all_actors[-c(65, 66, 867, 1268, 1669, 2070, 2471, 3272, 3673)]

# Find indices of elements containing "|" in front of the profits when we selected them
indices <- grep("\\|", all_profits)

# Remove elements containing "|" and now we will have nice numbers for each of the profits for each movie
all_profits <- all_profits[-indices]

# Positions to insert "N/A", we went through each movie and were able to indentify which movies from the website did not have any profits and so we imported N/A in its place
positions <- c(45,109, 149, 167, 174, 176, 222, 235, 236, 246, 250, 327, 334, 347, 378, 380, 397, 403, 405, 409, 423, 429, 438, 443, 451, 460, 466, 473, 494, 518, 556, 569, 588, 597, 601, 607, 610, 646, 657, 674, 680, 687, 732, 740, 757, 759, 767, 776, 778, 779, 790, 793, 794, 797, 802, 867, 874, 886, 908, 916, 946, 948, 980, 987, 992)

# Iterate over each position and insert "N/A" where needed in the code
for (pos in positions) {
  all_profits <- c(all_profits[1:(pos-1)], "N/A", all_profits[pos:length(all_profits)])
}
# Assign 4 actors to each movie since each movie has 4 actors exactly
iterations <- length(all_actors) %/% 4

# Initialize empty lists to store combined data based on the actors and number of actors 
combined_list <- vector("list", iterations)

# Iterate through the lists and then assign the actors, directors, raitngs, profit correctly to each movie and then display the data
for (i in 1:iterations) {
  start_idx <- (i - 1) * 4 + 1
  end_idx <- i * 4
  combined_list[[i]] <- list(
    Title = all_titles[i],
    Actor1 = all_actors[start_idx],
    Actor2 = all_actors[start_idx + 1],
    Actor3 = all_actors[start_idx + 2],
    Actor4 = all_actors[start_idx + 3],
    Director = all_directors[i],
    Rating = all_ratings[i],
    Profit = all_profits[i]
  )
}

# Convert the list to a data frame so it is better able to access
df <- do.call(rbind, combined_list)
# Convert the list to a data frame using the r bind function
df <- as.data.frame(do.call(rbind, combined_list))



# created a subset based on the rating greater than 8.6
subset_df <- subset(df, Rating > 8.6)


#Create a df that has movies with ratings 8.6 and higher
Rating_df <- subset(df, Rating >= 8.6, c("Title", "Actor1", "Actor2", "Actor3", "Actor4"))


# Create a data frame that only uses the director Steven Speilburg and then only find the actors and title. 
Director_df <- subset(df, Director == "Steven Spielberg", c("Title", "Actor1", "Actor2", "Actor3", "Actor4"))



# Reshape the data frame so that we are able to get the actor and then assign each movie they go to
Director_df_long <- pivot_longer(Director_df, cols = starts_with("Actor"), values_to = "Actor")

# Remove "Actor" from the names of the 'Actor' column so that we just get the actor and the movie they are assign to
Director_df_long$Actor <- gsub("Actor", "", Director_df_long$Actor)

# Remove the 'name' column
Director_df_long <- select(Director_df_long, -name)

# Order the data frame by Title
Director_df_long <- arrange(Director_df_long, Title)




# Switch the columns so that they become rows
switched_director_df_long <- Director_df_long[, c("Actor", "Title")]



#turns the data long so that it can be processed easier
network <- switched_director_df_long %>% 
  as_tbl_graph()



```
\vspace{4cm}  
## Connectedness Graph

- The next step after getting and processing the data was to organize it into an easily viewable format and we found that a connectedness graph created via VisNetwork was a good format. Creating a VisNetwork required us to move the data into start and end positions for each jump between movies and then it maps all of them between actors and movies. It then plots these onto a map where you can find the movies as little films and the actors as dots attached to them. This allows for an easier viewing process and shows the thought process behind a Bacon Number. We started off by doing a test run with a smaller data set using just Speilberg movies (seen below) and that went very well.


\vspace{4cm}  
```{r,echo=FALSE,warning=FALSE,message=FALSE}

# sets network up for making a network graph changing the network to a tibble
network %>% 
  activate(nodes) %>%
  mutate(degree = centrality_degree()) %>%
  as_tibble() %>%
  arrange(desc(degree))

# Makes a visnetwork using the data and binds that to the swithced director data 
vis_network <- network %>% 
  mutate(group = if_else(condition = name %in% unique(switched_director_df_long$Actor),
                         true = "Actor",
                         false = "Title")) %>%
  toVisNetworkData()
# Sets up the visnetwork visually and then allows to create a graph we slected the movie icon and then we are able to select the movies to be the main part to each graph, we then selected the different colors for each part, and then we are able to produce the graph
visNetwork(nodes=vis_network$nodes, edges = vis_network$edges,
           width = "100%", height = "600px",
           main = "Connectedness Graph of Spielberg") %>%
  visLayout(randomSeed = 1000) %>%
  addFontAwesome() %>%
  visGroups(groupname = "Title", shape = "icon",
            icon = list(code = "f008", color = "darkblue")) %>%
  visGroups(groupname = "Character", shape = "icon",
           icon = list(code = "f007", color ="red")) %>%
  visOptions(highlightNearest = list(enabled = TRUE, hover = TRUE),
             nodesIdSelection = TRUE) %>%
  visInteraction(navigationButtons = TRUE)
```
\vspace{4cm}  

\vspace{5cm}  

\vspace{5cm} 

- We then made a function where the user can input a director or a group of directors and can get a connectedness chart from the movies they directed in our data set. Below is an example using the first 10 directors in our data set and the function is easy to use given our data set here. We limited the data used to create these sample graphs because when attempted with all of the data provided it would take too long to process and would be unusable. We decided directors was an easy and effective way to limit searching because a lot of directors use the same actors already and it would keep the large chunks together instead of creating a large amount of small pieces.
\vspace{4cm}  
 
```{r,echo=FALSE,message=FALSE,message=FALSE}
# We are now able to select whichever director we want for the graph and this is mcuh more user friendly for finding results we want to know
Graph_Director = function(director)
{
  Director_df <- subset(df, Director == director, c("Title", "Actor1", "Actor2", "Actor3", "Actor4"))
  # Reshape the data frame
Director_df_long <- pivot_longer(Director_df, cols = starts_with("Actor"), values_to = "Actor")

# Remove "Actor" from the names of the 'Actor' column
Director_df_long$Actor <- gsub("Actor", "", Director_df_long$Actor)

# Remove the 'name' column
Director_df_long <- select(Director_df_long, -name)

# Order the data frame by Title
Director_df_long <- arrange(Director_df_long, Title)


  

# Switch the columns to rows 
switched_director_df_long <- Director_df_long[, c("Actor", "Title")]



#turns the data long so that it can be processed easier
network <- switched_director_df_long %>% 
  as_tbl_graph()

# sets network up for making a network graph changing the network to a tibble
network %>% 
  activate(nodes) %>%
  mutate(degree = centrality_degree()) %>%
  as_tibble() %>%
  arrange(desc(degree))

# Makes a visnetwork using the data and binds that to the swithced director data
vis_network <- network %>% 
  mutate(group = if_else(condition = name %in% unique(switched_director_df_long$Actor),
                         true = "Actor",
                         false = "Title")) %>%
  toVisNetworkData()

# Sets up the visnetwork visually and then allows to create a graph we slected the movie icon and then we are able to select the movies to be the main part to each graph, we then selected the different colors for each part, and then we are able to produce the graph
visNetwork(nodes=vis_network$nodes, edges = vis_network$edges,
           width = "100%", height = "600px",
           main = "Connectedness Graph of Selected Directors") %>%
  visLayout(randomSeed = 1000) %>%
  addFontAwesome() %>%
  visGroups(groupname = "Title", shape = "icon",
            icon = list(code = "f008", color = "darkblue")) %>%
  visGroups(groupname = "Character", shape = "icon",
           icon = list(code = "f007", color ="red")) %>%
  visOptions(highlightNearest = list(enabled = TRUE, hover = TRUE),
             nodesIdSelection = TRUE) %>%
  visInteraction(navigationButtons = TRUE) 
}
# We are now able to select whichever director we want only for the top 10 for the graph and this is mcuh more user friendly for finding results we want to know
Graph_Director(all_directors[1:10])
```
\vspace{4cm}  

## Hanks Numbers
- Instead of calculating a traditional "Bacon Number" our group decided to calculate a number for degrees of separation for a more relevant and connected actor in our data set, that being Tom Hanks. This observation was found in our connectedness graph shown previously. Below you can view the 6 least connected actors in our data set reaching all the way to 10 degrees of separation. The average degrees of separation among people is typically 3. This statement also holds relatively true regarding our data set and "Hanks Number" which is shown in our five number summary as well as the graph showcasing the distribution of "Hanks Numbers". 

\vspace{4cm}  
\vspace{5cm}  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(dplyr)
library(visNetwork)

# This code just takes the data frame and makes the graph so that it has 4 actors with each movie to each actor assign to the movie 4 times
df_long <- pivot_longer(df, cols = starts_with("Actor"), values_to = "Actor")
df_long$Actor <- gsub("Actor", "", df_long$Actor)
df_long <- select(df_long, -name)
df_long <- arrange(df_long, Title)
df_long <- df_long %>% select(Actor, Title)



# Create a graph object
graph <- graph.data.frame(df_long, directed = FALSE)

# Find the index of Tom Hanks in the graph
tom_hanks_index <- which(V(graph)$name == "Tom Hanks")

# Calculate shortest paths to Tom Hanks for all actors
hanks_numbers <- shortest.paths(graph, to = tom_hanks_index)

# Extract Hanks numbers for each actor
actors <- V(graph)$name
hanks_numbers_df <- data.frame(actor = actors, hanks_number = hanks_numbers / 2)

# Filter out movies from the list of "Hanks Numbers"
filtered_hanks_numbers_df <- hanks_numbers_df[!hanks_numbers_df$actor %in% all_titles, ]

# Remove actors that aren't connected to Tom Hanks
filtered_hanks_numbers_df <-  filtered_hanks_numbers_df[filtered_hanks_numbers_df$Tom.Hanks != "Inf", ]
# Remove the column labeled "actor"
filtered_hanks_numbers_df <- select(filtered_hanks_numbers_df, -actor)


# Arrange the results in descending order based on the "hanks_number" column
filtered_hanks_numbers_df <- arrange(filtered_hanks_numbers_df, desc(Tom.Hanks))

head(filtered_hanks_numbers_df)

# Create histogram that will take the hank number and then is able to find the mean and we are able to graph is nicely so that we see all of the numbers 1 through 10 and clean the graph up 
histogram <- ggplot(filtered_hanks_numbers_df, aes(x = Tom.Hanks)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black", alpha = 0.7) +  
  labs(title = "Histogram of Hanks Numbers",
       x = "Hanks Number",
       y = "Frequency") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),  # Center the title
        axis.text = element_text(size = 10),     # Adjust axis text size
        axis.title = element_text(size = 12),    # Adjust axis title size
        plot.margin = unit(c(1, 1, 1, 1), "cm")) +  # Add margin around the plot
  scale_x_continuous(breaks = seq(1, max(filtered_hanks_numbers_df$Tom.Hanks), by = 1)) +  # Use whole numbers on the x-axis starting from 1
  coord_cartesian(xlim = c(1, max(filtered_hanks_numbers_df$Tom.Hanks) + 1))  # Expand x-axis range starting from 1

# Calculate mean value
mean_value <- mean(filtered_hanks_numbers_df$Tom.Hanks)

# Add mean line
histogram <- histogram + geom_vline(xintercept = mean_value, color = "red", linetype = "dashed")

# Print histogram
print(histogram)
summary(filtered_hanks_numbers_df)

```
\vspace{5cm}  
\vspace{4cm}  
## Modifing the Game

- In order to change the way of interacting with the Hanks number we decided to add a filter based on movie rating to see what actors connect based on this factor. We pulled the movie ratings from the original data pull and kept this variable around in order to use as a filter later on. We decided to change the game based on rating because actors that associate with each other tend to appear in the same range of movie ratings as each other. Being that Tom Hanks is a well known actor in high end productions we thought that adding a filter that has movies greater than certain ratings would find us higher Hanks numbers. Because of this we know that our connectedness graph and actors that fit the Hanks number would not be affected as much as if we did it based on a different restriction such as profit or genre. Finally, in order to change this list we simply just change what rating we want to input and therefore make the list shrink or grow based on where and how wide the interval is.

\vspace{5cm}  

```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(igraph)
library(dplyr)

# Create filter so that you can find Hanks numbers for movies that fit certain ratings 
df_rating <- filter(df, df$Rating >=8.5)

# This code just takes the data frame and makes the graph so that it has 4 actors with each movie to each actor assign to the movie 4 times
df_long <- pivot_longer(df_rating, cols = starts_with("Actor"), values_to = "Actor")
df_long$Actor <- gsub("Actor", "", df_long$Actor)
df_long <- select(df_long, -name)
df_long <- arrange(df_long, Title)
df_long <- df_long %>% select(Actor, Title)



# Create a graph object
graph <- graph.data.frame(df_long, directed = FALSE)

# Find the index of Tom Hanks in the graph
tom_hanks_index <- which(V(graph)$name == "Tom Hanks")

# Calculate shortest paths to Tom Hanks for all actors
hanks_numbers <- shortest.paths(graph, to = tom_hanks_index)

# Extract Hanks numbers for each actor
actors <- V(graph)$name
hanks_numbers_df <- data.frame(actor = actors, hanks_number = hanks_numbers / 2)

# Filter out movies from the list of "Hanks Numbers"
filtered_hanks_numbers_df <- hanks_numbers_df[!hanks_numbers_df$actor %in% all_titles, ]

# Remove actors that aren't connected to Tom Hanks
filtered_hanks_numbers_df <-  filtered_hanks_numbers_df[filtered_hanks_numbers_df$Tom.Hanks != "Inf", ]
# Remove the column labeled "actor"
filtered_hanks_numbers_df <- select(filtered_hanks_numbers_df, -actor)

# Arrange the results in descending order based on the "hanks_number" column
filtered_hanks_numbers_df <- arrange(filtered_hanks_numbers_df, desc(Tom.Hanks))

print(filtered_hanks_numbers_df)


```
